NTM CT Scoring - Initial Agreement

### 2023-05-18 Stacey Martiniano/ntm_agreement.qmd
singleton scans

Cohen's Kappa for A vs. the gold standard was `r round(A$value,3)` (p = `r format.pval(A$p.value,eps = 0.001,digits = 3)`).

Cohen's Kappa for B vs. the gold standard was `r round(B$value,3)` (p = `r format.pval(B$p.value,eps = 0.001,digits = 3)`).

Cohen's Kappa for C vs. the gold standard was `r round(C$value,3)` (p = `r format.pval(C$p.value,eps = 0.001,digits = 3)`).

@@

Cohen's Kappa for A vs. themselves was `r round(A$value,3)` (p = `r format.pval(A$p.value,eps = 0.001,digits = 3)`).

Cohen's Kappa for B vs. themselves was `r round(B$value,3)` (p = `r format.pval(B$p.value,eps = 0.001,digits = 3)`).

Cohen's Kappa for C vs. themselves was `r round(C$value,3)` (p = `r format.pval(C$p.value,eps = 0.001,digits = 3)`).

@@

>>>>

Overall Cohen's Kappa for A vs. the gold standard was `r round(A$value,3)` (p = `r format.pval(A$p.value,eps = 0.001,digits = 3)`).

Overall Cohen's Kappa for B vs. the gold standard was `r round(B$value,3)` (p = `r format.pval(B$p.value,eps = 0.001,digits = 3)`).

Overall Cohen's Kappa for C vs. the gold standard was `r round(C$value,3)` (p = `r format.pval(C$p.value,eps = 0.001,digits = 3)`).

@@

Overall Cohen's Kappa for A vs. themselves was `r round(A$value,3)` (p = `r format.pval(A$p.value,eps = 0.001,digits = 3)`).

Overall Cohen's Kappa for B vs. themselves was `r round(B$value,3)` (p = `r format.pval(B$p.value,eps = 0.001,digits = 3)`).

Overall Cohen's Kappa for C vs. themselves was `r round(C$value,3)` (p = `r format.pval(C$p.value,eps = 0.001,digits = 3)`).

@@

# Singleton scans

```{r}
# Gold standard data
df = data %>% 
  arrange(scan_id, scorer) %>%
  filter(!(scan_id %in% dups$original_ssid) & 
           !(scan_id %in% training$Cffid.Scoring.Set)) %>%
  select(scorer, scan_id,bronchiectasis_rul:atelectasis___6) %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
                             names_to = c("feature", "location"),
                             names_pattern = "(.*)_(.*)$"
  ) %>% 
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  ) 
df$location <- factor(df$location,
                       levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", 
                                  "lul", "rll", "rml", "rul"),
                       labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", 
                                  "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
)
# One column per scorer
df <- df %>% 
  pivot_wider(names_from = scorer, values_from = value) %>%
  arrange(feature,location)
```

```{r}
df_bronch = df %>% filter(feature=="Bronchiectasis")
fk = kappam.fleiss(df_bronch[,c("A","B","C")])
# Plot
df_bronch %>%
  select(scan_id,feature, location,A:C) %>%
  pivot_longer(A:C) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Overall Fleiss' Kappa for all 15 singleton scans was `r round(fk$value,3)` (p = `r format.pval(fk$p.value,eps = 0.001,digits = 3)`).

```{r}
df_other = df %>% filter(feature!="Bronchiectasis")
# Check agreement with GS column
df_other[,c("A","B","C")] = lapply(df_other[,c("A","B","C")],factor,
                                   levels = c("Unchecked", "Checked"),
                                   labels = c("Absent","Present"))
# Three-way agreement
df_other$`A vs. B`=factor(df_other$A == df_other$B,levels = c(F,T),labels = c("Disagree","Agree"))
df_other$`A vs. C`=factor(df_other$A == df_other$C,levels = c(F,T),labels = c("Disagree","Agree"))
df_other$`B vs. C`=factor(df_other$B == df_other$C,levels = c(F,T),labels = c("Disagree","Agree"))
# Plot
df_other %>%
  select(scan_id,feature, location, `A vs. B`:`B vs. C`) %>%
  pivot_longer(`A vs. B`:`B vs. C`) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  facet_grid(rows = vars(feature),cols = vars(scan_id))
# Tables
df_other %>%
  summarise(across(`A vs. B`:`B vs. C`,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with themselves")
df_other %>%
  group_by(scan_id) %>%
  summarise(across(`A vs. B`:`B vs. C`,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with themselves")
df_other %>%
  group_by(feature) %>%
  summarise(across(`A vs. B`:`B vs. C`,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with themselves")
df_other %>%
  group_by(scan_id,feature) %>%
  summarise(across(`A vs. B`:`B vs. C`,~mean(.x == "Agree",na.rm = T)),.groups = "drop") %>%
  kable(.,digits=3,caption = "Proportion of agreement with themselves")
# Heatmaps
df_other %>%
  group_by(scan_id) %>%
  summarise(across(`A vs. B`:`B vs. C`,~mean(.x == "Agree",na.rm = T)),.groups = "keep") %>%
  column_to_rownames("scan_id") %>%
  pheatmap(.,cluster_rows = F,cluster_cols = F)
df_other %>%
  group_by(feature) %>%
  summarise(across(`A vs. B`:`B vs. C`,~mean(.x == "Agree",na.rm = T)),.groups = "keep") %>%
  column_to_rownames("feature") %>%
  pheatmap(.,cluster_rows = F,cluster_cols = F)
df_other %>%
  group_by(scan_id,feature) %>%
  summarise(across(`A vs. B`:`B vs. C`,~mean(.x == "Agree",na.rm = T)),.groups = "keep") %>%
  unite(ids,scan_id,feature,na.rm = T,sep = " ") %>%
  column_to_rownames("ids") %>%
  pheatmap(.,cluster_rows = F,cluster_cols = F)
```
